---
title: "Live Coding - EDA"
author: "Mandip"
date: "30/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

This doc stores all of the code for the live coding portion of your class

Lets deal with missing values first 
Take a quick look at our data

```{r, eval=FALSE}
# Copy Paste This
data(penguins)
summary(penguins)  
```

When checking for missing values there are 2 things that you can do. 
1) Delete them all (not always suggested) 

```{r, eval = FALSE}
# Type this
cleaned_data_set <- penguins %>% 
  drop_na()
```

Don't recommend this however
2) Instead subset those NA values take a quick look and see if you can use any of them 
Instead what you can do is isolate the NA give em a look 
And see if you can replace the missing values with something
So that you can keep some of the useful other data


```{r, eval=FALSE}
# Type This
na_values <- penguins %>% 
  filter_all(any_vars(is.na(.)))

```

```{r, eval=FALSE}
# Now lets take a quick look at that data now  
# Copy paste this in
view(na_values)
summary(na_values)
```

From first look most of the NA Values are are just missing sex and that's all 
For that reason you probably just want to drop the rows that are missing the values 
for measurements for the bill_length and flipper_length

How to do this?
Subset the values you want to drop
```{r, eval = FALSE}
na_to_drop <- na_values %>% 
  filter(is.na(bill_length_mm))

```

So lets just subset those 2 records out 
Only drop the records that do not have a value for bill length 

```{r, eval = FALSE}
cleaned_data_set <- penguins %>% 
  filter(!is.na(bill_length_mm))

```



